Errata

### 2025-04-04 tex/Introduction.tex
Refine methodology and results discussion sections for clarity and accuracy
- Updated the methodology section to enhance the description of microbial community data analysis techniques, ensuring consistency in terminology and clarity in the explanation of statistical methods.
- Revised the results discussion to improve the flow of information regarding biocrusts' impact on soil aggregate stability, emphasizing their role in arid ecosystems and correcting citation formatting.
- Adjusted references to ensure proper citation style and accuracy throughout the text.

However, as climate humidity increases along a gradient towards more temperate conditions, vegetation competes more effectively and biocrusts are often relegated to resource-limited niches \citep{Büdel2016}. In temperate regions, biocrusts stablishes on bare soils or soils with minimal plant development, where conditions such as high salinity, low nutrient availability, and limited water availability mirror the limiting conditions of arid landscapes \citep{Corbin2020}. Thus, the interplay between biocrusts, microbial communities, and plant roots shifts along this climatic gradient, diminishing, but not eliminating, the protagonism of biocrusts on soil stability, structure and size distribution of soil aggregates.

>>>>

However, as climate humidity increases along a gradient towards more temperate conditions, vegetation competes more effectively and biocrusts are often relegated to resource-limited niches \citep{Budel2016}. In temperate regions, biocrusts stablishes on bare soils or soils with minimal plant development, where conditions such as high salinity, low nutrient availability, and limited water availability mirror the limiting conditions of arid landscapes \citep{Corbin2020}. Thus, the interplay between biocrusts, microbial communities, and plant roots shifts along this climatic gradient, diminishing, but not eliminating, the protagonism of biocrusts on soil stability, structure and size distribution of soil aggregates.
